Predicted cardiovascular risk for US adults with diabetes, chronic kidney disease, and \u2265 65 years of age

### 2020-10-29 README.Rmd
still prepping for JACC submission

2. This project is built around `drake`, a workflow package. To produce every target in the drake workflow, run `r_make()` in your console.

3. Allow Rstudio to access the internet if prompted, as `r_make()` will be downloading NHANES data from the NHANES website while it produces the manuscript.

4. `r_make()` will build every target, ending with the manuscript and finally the `README.md` file. Simply open the file 'doc/ACCAHA_BP_groups.docx' to see the manuscript you built.

@@

3. Save your changes to the `R/plan.R` file and then run `r_make()` in your console.

>>>>

2. This project is built around `drake`, a workflow package. To produce every target in the drake workflow, run `drake::r_make()` in your console.

3. Allow Rstudio to access the internet if prompted, as `drake::r_make()` will be downloading NHANES data from the NHANES website while it produces the manuscript.

4. `drake::r_make()` will build every target, ending with the manuscript and finally the `README.md` file. Simply open the file 'doc/ACCAHA_BP_groups.docx' to see the manuscript you built.

@@

3. Save your changes to the `R/plan.R` file and then run `drake::r_make()` in your console.

### 2020-10-29 doc/ACCAHA_BP_groups.Rmd
include GH link
still prepping for JACC submission

@@

`r NHANES()` sampling weights, which were calculated as the inverse probability of being selected for the survey, were used in all calculations to obtain nationally representative estimates of the non-institutionalized US population. P-values were two-sided. Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages [@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue]. The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current study.

>>>>

_Note:_ This illustration is not the same as the central illustration in the paper. A different version is used in order to adhere to a publication agreement: "Excluding abstracts, none of the paper's contents have been previously published."

@@

`r NHANES()` sampling weights, which were calculated as the inverse probability of being selected for the survey, were used in all calculations to obtain nationally representative estimates of the non-institutionalized US population. P-values were two-sided. Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages [@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue]. The first author's GitHub repository (https://github.com/bcjaeger/ACC-AHA-BP-guideline-groups) provides code to reproduce the current study.
